---
title: "W_UP_01"
author: "Juan Padilla"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Position is a categorical variable. Pushups is a numerical variable. I will do an analysis that explains push ups based on position.


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

There is pushups on the y-axis of the box plot. While there is the positions on the x-axis. On the box plotm there is a large segment on each whisker plot. The average push-ups for the positions appears to be different. The skill position appears to do more pushups based off of the y-axis. (pushups)

### Numerical Descriptive Results

```{r}
favstats(pushups~position,data=mydata)
```

The median of the positions is different, whereas the skill is significantly greater. The max amount of pushuos in the line position was 34 opposed to the skill position maximum of 108. The line position also had a lower mean average of 17.125 and the skill had the higher mean average of 49.72727.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The t value is -5.43241. The df value is 27.079. The P value is 0.0000009421. Alt hypothesis is shown; the alternate hypothesis states "true difference in means between group LINE and group SKILL is not equal to 0" The mean for Line is 17.1250 and the mean for Skill is 49.72727.


# Discussion and Conclusion

We were presented with a null hypothesis and alternate hypothesis; Null being no difference between the average number of pushups of LINE vs Skill players, and the alternate being the average number of pushups done by the LINE players is statistacally different that that of SKILL players. When checking our findings according to the our methodology, we find that SKILL position players are able to do more pushups opposed to LINE players. They were able to as well perform at a greater mean average and median average. When comparing the inferential results we find that we have a significantly low value of 0.0000009421 which although our null hypothesis is possible we are able to ignore it because of it holds a significantly low value.

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

